---
title: "Analysis"
---

First of all, we generated the data that would be useful to us from TURKSTAT's website. After downloading the data as an Excel file, we changed the positions of the columns and raws, making it easier to work on it. Next, we anchored the rows and columns of the data so that R could read them. Finally, we created column headings for the cities.\
\
Loading necessary libraries :

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

library(readxl)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggrepel)
library(reshape2)
library(gridExtra)

```

Load the data:

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

library(readxl)
url <- "https://github.com/emu-hacettepe-analytics/emu430-fall2023-team-quant_flare/raw/master/Foreign_child_by_year.xlsx"
temp_file <- tempfile(fileext = ".xlsx")
download.file(url, temp_file, mode = "wb")
dataset <- read_excel(temp_file)

head(dataset)
str(dataset)

summary(dataset)
```

# EDA ANALYSE

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

head(dataset)
str(dataset)
summary(dataset)


# Veri çerçevesini oluştur
mean_values <- dataset %>%
  gather(key = "Year", value = "Value", -City) %>%
  group_by(Year) %>%
  summarize(mean_value = mean(Value, na.rm = TRUE))

# Veri çerçevesini kontrol et
print(mean_values)

# Drawing a boxplot of values by city
dataset_long <- melt(dataset, id.vars = "City")
ggplot(dataset_long, aes(x = variable, y = value)) +
  geom_boxplot() +
  labs(title = "Value Distribution of Cities",
       x = "Year",
       y = "Value") +
  theme_minimal()

# Showing ranked values of cities for 2022
dataset_2022 <- dataset %>%
  select(City, `2022`) %>%
  arrange(desc(`2022`))

ggplot(dataset_2022, aes(x = reorder(City, `2022`), y = `2022`)) +
  geom_bar(stat = "identity") +
  labs(title = "Ranked Values of Cities by 2022",
       x = "City",
       y = "Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Bring related charts together
grid.arrange(ggplot(dataset_long, aes(x = variable, y = value)) +
               geom_boxplot() +
               labs(title = "Value Distributions of Cities",
                    x = "Year",
                    y = "Value") +
               theme_minimal(),
             ggplot(dataset_2022, aes(x = reorder(City, `2022`), y = `2022`)) +
               geom_bar(stat = "identity") +
               labs(title = "Ranked Values of Cities by 2022",
                    x = "City",
                    y = "Value") +
               theme_minimal() +
               theme(axis.text.x = element_text(angle = 45, hjust = 1)),
             ncol = 1)
               
```

Visualization to see trends We visualized the data set as a line graph. In this way , data visualization of all cities was achieved at once.

```{r, message=FALSE, results='asis'}
#| warning: false
#| code-summary: "Show the code"
#| code-fold: true

# We converted the data to long format for ggplot2
library(tidyr)
foreign_child_long <- gather(dataset, key = "Year", value = "Value", -City)

# Code for Printing the structure and head of the data frame for inspection
str(foreign_child_long)
head(foreign_child_long)

# Converting the 'Year' column to a factor for correct ordering
foreign_child_long$Year <- factor(foreign_child_long$Year, levels = c("2014", "2015", "2016", "2017", "2018", "2019", "2020", "2021", "2022"))

# Checking the levels of the 'Year' factor
levels(foreign_child_long$Year)

# Creating a line plot
library(ggplot2)
ggplot(foreign_child_long, aes(x = Year, y = Value, group = City, color = City)) +
  geom_line() +
  geom_point() +
  labs(title = "Foreign Child Population Over the Years",
       x = "Year",
       y = "Population") +
  theme_minimal()

```

As we expected, the number in densely populated cities such as Istanbul and Ankara was much higher than other cities. But what was surprising was the density in Antalya. Antalya, which is not among the top 5 provinces of Turkey in terms of population density, had a higher density than expected. Having all 81 cities on a single line chart did not provide a very efficient analysis facility. We added the columns of the data set and plotted the total number between 2014 and 2022 on a line chart. In this way, a trend that is the average of all cities can be observed.

```{r}
# We converted the data to long format for ggplot2
library(tidyr)
foreign_child_long <- gather(dataset, key = "Year", value = "Value", -City)

# Code for Printing the structure and head of the data frame for inspection
str(foreign_child_long)
head(foreign_child_long)

# Converting the 'Year' column to a factor for correct ordering
foreign_child_long$Year <- factor(foreign_child_long$Year, levels = c("2014", "2015", "2016", "2017", "2018", "2019", "2020", "2021", "2022"))

total_foreign_child <- foreign_child_long %>%
  group_by(Year) %>%
  summarise(Total_Value = sum(Value, na.rm = TRUE))

# Creating a line plot for the total values
ggplot(total_foreign_child, aes(x = Year, y = Total_Value)) +
  geom_line() +
  geom_point() +
  labs(title = "Total Foreign Child Population Over the Years",
       x = "Year",
       y = "Total Population") +
  theme_minimal() +
  scale_y_continuous(labels = scales::comma_format(scale = 1e-3, suffix = "K"))
```

In the light of the graph , it can be easily seen that there is an increasing trend in the number of foreign babies born in the last 10 years.
